Items: English

### 2021-11-05 preregistration_changes.Rmd
- implemented feedback from Nick - updated analyses - provided additional plots for control variables

When reading the documentation of the data, I thought the following variables were varying, when in fact they were assessed only at one wave, namely the first wave:

- Employment status

## To-Do

- Analyses
	- Missingness
		- Impute missing values
		- Determine amount of missingness
		- Replace values where I know they're 0
	- Add factor scores
	- CFA
		- Add results

>>>>

I originally planned to include the following variables as varying covariates. I thought they were measured at several/all waves. However, upon seeing the actual data I realized this wasn't the case. I hence included them as stable covariates.

This includes (a) text-based media news consumption, (b) video-based media news consumption, (c) residency is Vienna, (d) self-reported physical health, (e) living space (in squaremeter), (f) access to balcony, (g) access to garden, (h) employment status, (i) disposition to take risks, and (j) locus of control.

The following variables I originally planned to include as control variables. However, their inclusion led to the deletion of too many cases/observations. I hence decided against their inclusion. This includes (a) household size, (b) work hours per week, (c) home office, (d) household income.

## Analyses

I planned to conduct also the following analyses. I the time of writing, I simply hadn't yet found the time to do so.

	- Impute missing values
	- Report CFAs for scales
	- Run analyses using factor scores
